The Solar System: an Exercise in Numerical Integration \\ \hrulefill\small{ FYS3150: Computational Physics }\hrulefill

### 2016-10-23 Project3/article/article.tex
Added figures

>>>>

The object-oriented model for the solar system that has been built is very flexible, as the reader will soon come to know. We start by constructing some simple models with two and three bodies, then the entire solar system, and lastly, simulate the perihelion precession of Mercury, as discussed in the theory section.
